Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2019-11-09 paper-bedpca.tex
add pipeline

>>>>

\begin{figure}[!htpb]
\centerline{\includegraphics[width=0.4\textwidth]{PCA-pipeline.pdf}}
\caption{Pipeline for computing Principal Components (PCs) using R packages bigsnpr and bigutilsr. [ADD VISUAL INSPECTION? QC? IN THE LEGEND?]
\label{fig:pipeline}}
\end{figure}

In this work, we compiled different pitfalls that can occur with analyses related to Principal Component Analysis (PCA) of genetic data. We then investigated possible solutions to these pitfalls and choose the ones that we thought to be the most relevant both with respect to properties such as accuracy and robustness, but also that are fast and easy to use. We then implemented these solutions in open-source R packages that are available for anyone to use.

As a general recommendation for computing PCA, we show some pipeline in figure \ref{fig:pipeline}. [DESCRIBE ALL STEPS?]
